---
title: NextKids pilot embeddings -second run
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: true
    code_folding: hide 
---

******
******

```{r setup, include = F}
# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(ggplot2)
library(stringr)
library(forcats)
library(jsonlite)
library(vegan)
library(shapes)
library(langcog)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = T, tidy = F, fig.height = 4)
```  

# young-middle-old{.tabset}
read in embeddings and join in item information
```{r}
young = read.csv("model_34.csv", header = FALSE) %>%
  mutate(group = "young")
middle = read.csv("model_56.csv", header = FALSE) %>%
  mutate(group = "middle")
old = read.csv("model_78.csv", header = FALSE) %>%
  mutate(group = "old")
adult = read.csv("model_adults.csv", header = FALSE) %>%
  mutate(group = "adult")

labs =read.table("labels.txt", header = FALSE) %>%
      rename(item = V1) %>%
      mutate(item = lapply(str_split(item, ".jpg"), 
                                   function(x) {x[1]}))
d = cbind(labs, young) %>%
  rbind(cbind(labs,middle)) %>%
  rbind(cbind(labs,old)) %>%
  rbind(cbind(labs,adult)) %>%
  rename(x = V1,
         y = V2) %>%
  mutate(item = as.factor(unlist(item))) %>%
  mutate(group = fct_relevel(group, "young", "middle", "old")) 
```

```{r}
dict = read.csv("../image_dict.csv") %>%
  select(images, type, theme) %>%
  rename(item = images)

d  = left_join(d, dict)
```


## Points
```{r}
ggplot(d, aes(x = x, y = y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_grid(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "bottom")
```

## Labels
```{r}
ggplot(d, aes(x = x, y = y)) +
   geom_text(aes(label=item), size = 3) +
   facet_grid(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())
```

# median age split{.tabset}
read in embeddings
```{r}
low = read.csv("model_lowage.csv", header = FALSE) %>%
  mutate(group = "low")
high = read.csv("model_highage.csv", header = FALSE) %>%
  mutate(group = "high")


d.m.age= cbind(labs, low) %>%
  rbind(cbind(labs,high)) %>%
  rename(x = V1,
         y = V2) %>%
  mutate(item = as.factor(unlist(item))) %>%
  mutate(group = fct_relevel(group, "low", "high")) %>%
  left_join(dict)
```

## Points
```{r}
ggplot(d.m.age, aes(x = x, y = y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_wrap(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "bottom")

```

## Labels
```{r}
ggplot(d.m.age, aes(x = x, y = y)) +
   geom_text(aes(label=item), size = 3) +
   facet_wrap(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())
```

# median vocab split{.tabset}
read in embeddings 
```{r}
low = read.csv("model_lowvocab.csv", header = FALSE) %>%
  mutate(group = "low")
high = read.csv("model_highvocab.csv", header = FALSE) %>%
  mutate(group = "high")

d.m.vocab = cbind(labs, low) %>%
  rbind(cbind(labs,high)) %>%
  rename(x = V1,
         y = V2) %>%
  mutate(item = as.factor(unlist(item))) %>%
  mutate(group = fct_relevel(group, "low", "high")) %>%
  left_join(dict)
```

## Points
```{r}
ggplot(d.m.vocab, aes(x = x, y = y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_wrap(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "bottom")
```

## Labels
```{r}
ggplot(d.m.vocab, aes(x = x, y = y)) +
   geom_text(aes(label=item), size = 3) +
   facet_wrap(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey",
                                        fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())
```

# group distance
## young-middle-old split
```{r}
# all pairs of items with their feature info
all.pairs = combn(labs$item, 2) %>%
  t(.) %>%
  as.data.frame(.) %>%
  rename(item1 = V1,
          item2 = V2) %>%
  mutate(item1 = as.factor(unlist(item1)),
         item2 = as.factor(unlist(item2))) %>%
  left_join(dict, by=c("item1" = "item"))%>%
  rename(type1 = type,
         theme1 = theme) %>%
  left_join(dict, by=c("item2" = "item")) %>%
  rename(type2 = type,
         theme2 = theme) %>%
    mutate(item1 = as.factor(unlist(item1)),
         item2 = as.factor(unlist(item2)))

getMeanDist <- function(age, semantic_group, d){

  # rename colums for semantitc group
  if (semantic_group == "type") {
    g1 = "bird"
    g2 = "mammal"
    these.pairs = all.pairs %>%
      rename(target1 = type1,
             target2 = type2)
  } else if (semantic_group == "theme") {
    g1 = "farm"
    g2 = "wild"
    these.pairs = all.pairs %>%
      rename(target1 = theme1,
             target2 = theme2) 
  }
  
  # coordinates for this age group
  coords = d %>%
    filter(group == age) %>%
    select(item,x,y)
  
  # merge in item coordinates for this age group
  these.pairs.with.coords = these.pairs %>%
    select(item1, item2, target1, target2) %>%
    left_join(coords, by=c("item1" = "item")) %>%
    rename(x1 = x,
           y1 = y) %>%
    left_join(coords, by=c("item2" = "item")) %>%
    rename(x2 = x,
           y2 = y)
  
  # get dists
  mean.dists = these.pairs.with.coords %>%
       rowwise() %>%
       mutate(dist = sqrt((x2-x1)^2 + (y2-y1)^2)) %>%
       mutate(collapse_group = ifelse(target1 == g1 & target2 == g1, g1,
                                    ifelse(target1 == g2 & target2 == g2, g2, 
                                           paste0("between_", semantic_group)))) %>%
       group_by(collapse_group)  %>%
       multi_boot_standard(column = "dist", na.rm = T) %>%
       mutate(age_group = age,
              semantic_group = semantic_group)
  mean.dists
}

# all combos of interest
all.groups = expand.grid(c("young", "middle", "old", "adult"),
            c("theme","type")) 
  
all.means <- map2(all.groups$Var1,
          all.groups$Var2, getMeanDist, d) %>%
          bind_rows()

ggplot(all.means, aes(x = age_group, y = mean)) +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  facet_wrap(~collapse_group) +
  theme_bw()

relative.means = all.means %>%
  select(collapse_group, mean, age_group) %>%
  spread(collapse_group, mean) %>%
  mutate(relative_bird = bird/between_type,
         relative_mammal = mammal/between_type,
         relative_farm = farm/between_theme,
         relative_wild = wild/between_theme) %>%
  select(-between_theme, -between_type, -farm, -mammal, -wild, -bird) %>%
  gather("group", "value", -1)

ggplot(relative.means, aes(x = age_group, y = value)) +
  geom_bar(stat ="identity") +
  facet_wrap(~group) +
  theme_bw()
```

## median age
```{r}
# all combos of interest
all.groups = expand.grid(c("low", "high"),
            c("theme","type")) 
  
all.means <- map2(all.groups$Var1,
          all.groups$Var2, getMeanDist, d.m.age) %>%
          bind_rows() 

ggplot(all.means, aes(x = age_group, y = mean)) +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  facet_wrap(~collapse_group) +
  theme_bw()

relative.means = all.means %>%
  select(collapse_group, mean, age_group) %>%
  spread(collapse_group, mean) %>%
  mutate(relative_bird = bird/between_type,
         relative_mammal = mammal/between_type,
         relative_farm = farm/between_theme,
         relative_wild = wild/between_theme) %>%
  select(-between_theme, -between_type, -farm, -mammal, -wild, -bird) %>%
  gather("group", "value", -1)

ggplot(relative.means, aes(x = age_group, y = value)) +
  geom_bar(stat ="identity") +
  facet_wrap(~group) +
  theme_bw()

```

## median vocab
```{r}
# all combos of interest
all.groups = expand.grid(c("low", "high"),
            c("theme","type")) 
  
all.means <- map2(all.groups$Var1,
          all.groups$Var2, getMeanDist, d.m.vocab) %>%
          bind_rows() 

ggplot(all.means, aes(x = age_group, y = mean)) +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  facet_wrap(~collapse_group) +
  theme_bw()

relative.means = all.means%>%
  select(collapse_group, mean, age_group) %>%
  spread(collapse_group, mean) %>%
  mutate(relative_bird = bird/between_type,
         relative_mammal = mammal/between_type,
         relative_farm = farm/between_theme,
         relative_wild = wild/between_theme) %>%
  select(-between_theme, -between_type, -farm, -mammal, -wild, -bird) %>%
  gather("group", "value", -1)

ggplot(relative.means, aes(x = age_group, y = value)) +
  geom_bar(stat ="identity") +
  facet_wrap(~group) +
  theme_bw() 
```


# procrustes transformations

## young-middle-old split
```{r, eval = F}
adult = filter(d, group == "adult") %>%
  select(x, y) %>%
  as.matrix()

young = filter(d, group == "young") %>%
  select(x, y) %>%
  as.matrix()

middle = filter(d, group == "middle") %>%
  select(x, y) %>%
  as.matrix()

old = filter(d, group == "old") %>%
  select(x, y) %>%
  as.matrix()

## procOPA 
ya = procOPA(young, adult)
ma = procOPA(middle, adult)
oa = procOPA(old, adult)

rd = rbind(
cbind(ya$Ahat[,'x'],ya$Ahat[,'y'],ya$Bhat[,1],ya$Bhat[,2]),
cbind(ma$Ahat[,'x'],ma$Ahat[,'y'],ma$Bhat[,1],ma$Bhat[,2]),
cbind(oa$Ahat[,'x'],oa$Ahat[,'y'],oa$Bhat[,1],oa$Bhat[,2]))  %>%
  as.data.frame() %>%
  mutate(group =  c(rep("young", 16), rep("middle", 16), rep("old", 16)))

names(rd) = c("x1", "y1", "x2", "y2", "group")

means = rd %>%
  mutate(group = as.factor(group)) %>%
  mutate(dist = sqrt((x2-x1)^2 + (y2-y1)^2))  %>%
  group_by(group) %>%
  multi_boot_standard(column = "dist", na.rm = T)

ggplot(means, aes(x= dist)) +
  geom_histogram() +
  facet_wrap(~group)
# xs
cor(ya$Ahat[,'x'], ya$Bhat[,1])
cor(ma$Ahat[,'x'], ma$Bhat[,1])
cor(oa$Ahat[,'x'], oa$Bhat[,1])

# ys
cor(ya$Ahat[,'y'],ya$Bhat[,2])
cor(ma$Ahat[,'y'],ma$Bhat[,2])
cor(oa$Ahat[,'y'],oa$Bhat[,2])

## procrustes 
ya2 = procrustes(young, adult)
ma2 = procrustes(middle, adult)
oa2 = procrustes(old, adult)

cor(ya2$X[,'x'], ya2$Yrot[,1])
cor(ma2$X[,'x'], ma2$Yrot[,1])
cor(oa2$X[,'x'], oa2$Yrot[,1])

cor(ya2$X[,'y'], ya2$Yrot[,2])
cor(ma2$X[,'y'], ma2$Yrot[,2])
cor(oa2$X[,'y'], oa2$Yrot[,2])

rd = rbind(
      cbind(ya2$X[,'x'],ya2$X[,'y'],ya2$Yrot[,1],ya2$Yrot[,2]),
      cbind(ma2$X[,'x'],ma2$X[,'y'],ma2$Yrot[,1],ma2$Yrot[,2]),
      cbind(oa2$X[,'x'],oa2$X[,'y'],oa2$Yrot[,1],oa2$Yrot[,2]))  %>%
      as.data.frame() %>%
      mutate(group =  c(rep("young",16), rep("middle", 16), rep("old", 16)),
             item = unlist(rep(labs$item,3)) )%>%
               left_join(dict)

names(rd)[1:5] = c("x1", "y1", "x2", "y2", "group")

m = rd %>%
  mutate(group = as.factor(group)) %>%
  mutate(dist = sqrt((x2-x1)^2 + (y2-y1)^2))  %>%
  group_by(group, theme, type) %>%
  multi_boot_standard(column = "dist", na.rm = T) %>%
  kable()

ggplot(rd, aes(x = x1, y = y2)) +
   geom_text(aes(label=item), size = 3) +
   facet_grid(pair~group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())

ggplot(m, aes(y=mean, x = group)) +
   geom_point( size = 3) +
   facet_grid(type~theme) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())
```

##  median vocab split
```{r, eval = F}
low = filter(d.m.vocab, group == "low") %>%
  select(x, y) %>%
  as.matrix()

high = filter(d.m.vocab, group == "high") %>%
  select(x, y) %>%
  as.matrix()

# procOPA
m = procOPA(low, adult)
n = procOPA(high, adult)

cor(m$Ahat[,'x'], m$Bhat[,1])
cor(n$Ahat[,'x'], n$Bhat[,1])

cor(m$Ahat[,'y'], m$Bhat[,2])
cor(n$Ahat[,'y'], n$Bhat[,2])

# procrustes
m = procrustes(low, adult)
n = procrustes(high, adult)

cor(m$X[,'x'], m$Yrot[,1])
cor(n$X[,'x'], n$Yrot[,1])

cor(m$X[,'y'], m$Yrot[,2])
cor(n$X[,'y'], n$Yrot[,2])


ggplot(all.pairs, aes(x = x, y = y)) +
   geom_text(aes(label=item), size = 3) +
   facet_grid(pair~group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank())
```


## median age split
```{r, eval = F}
low = filter(d.m.age, group == "low" ) %>%
  select(x, y) %>%
  as.matrix()

high = filter(d.m.age, group == "high" ) %>%
  select(x, y) %>%
  as.matrix()

# procOPA
m = procOPA(low, adult)
n = procOPA(high, adult)

cor(m$Ahat[,'x'], m$Bhat[,1])
cor(n$Ahat[,'x'],n$Bhat[,1])

cor(m$Ahat[,'y'], m$Bhat[,2])
cor(n$Ahat[,'y'], n$Bhat[,2])


# procrustes
m = procrustes(low, adult)
n = procrustes(high, adult)

cor(m$X[,'x'], m$Yrot[,1])
cor(n$X[,'x'], n$Yrot[,1])

cor(m$X[,'y'], m$Yrot[,2])
cor(n$X[,'y'], n$Yrot[,2])
```

## Procrustes on young and middle only

```{r}
young = filter(d, group == "young") %>%
  select(x, y) %>%
  as.matrix()

middle = filter(d, group == "middle") %>%
  select(x, y) %>%
  as.matrix()

ym = procOPA(young, middle)
m = rbind(ym$Ahat,ym$Bhat) %>%
  as.data.frame() %>%
  mutate(group = c(rep("young",16), rep("middle", 16)),
         item = c(unlist(labs$item), unlist(labs$item))) %>%
  left_join(dict)

ym = procrustes(young, middle)
m = rbind(ym$X,ym$Yrot) %>%
  as.data.frame() %>%
  mutate(group = c(rep("young",16), rep("middle", 16)),
         item = c(unlist(labs$item), unlist(labs$item))) %>%
  left_join(dict)
```


## Points
```{r}
ggplot(m, aes(x = x, y = y, color = type)) +
   geom_point(size = 3) +
   facet_grid(~group, scales = "free") +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "bottom")
```

## Labels
```{r}
ggplot(m, aes(x = x, y = y)) +
   geom_text(aes(label=item, color = type), size = 3) +
   facet_grid(~group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title = element_blank(),
        axis.text = element_blank(),
        axis.ticks = element_blank(),
        legend.position = "none")
```

## young-middle-old split
```{r}
# all pairs of items with their feature info
all.pairs2 = expand.grid(unlist(labs$item),unlist(labs$item)) %>%
  rename(item1 = Var1,
         item2 = Var2)

getMeanDist2 <- function(age, d){
  # coordinates for this age group
  coords = d %>%
    filter(group == age) %>%
    select(item,x,y)
  
  # merge in item coordinates for this age group
  these.pairs.with.coords = all.pairs2 %>%
    select(item1, item2) %>%
    left_join(coords, by=c("item1" = "item")) %>%
    rename(x1 = x,
           y1 = y) %>%
    left_join(coords, by=c("item2" = "item")) %>%
    rename(x2 = x,
           y2 = y)
  
  # get dists
  mean.dists = these.pairs.with.coords %>%
       rowwise() %>%
       mutate(dist = sqrt((x2-x1)^2 + (y2-y1)^2)) %>%
       mutate(group = age)

  mean.dists
}


all.dists <- map(c("young", "middle", "adult"), getMeanDist2, d) %>%
          bind_rows() %>%
  left_join(dict, by=c("item1" = "item"))%>%
  rename(type1 = type,
         theme1 = theme) %>%
  left_join(dict, by=c("item2" = "item")) %>%
  rename(type2 = type,
         theme2 = theme) 

### THEME
all.dists.item.ms = all.dists %>%
    group_by(item1, theme2, group) %>%
    summarize(mean = mean(dist)) 
    
all.dists.item.ms.gp = all.dists.item.ms %>%
  left_join(dict, by=c("item1" = "item")) %>%
  rename(type1 = type,
         theme1 = theme) %>%
  select(group, item1, theme1, theme2, mean) %>%
  mutate(category = ifelse(theme1 == theme2, "within", "between")) %>%
  ungroup() %>%
  select(-theme1, -theme2) %>%
  group_by(group, item1) %>%
  spread(category, mean) %>%
  mutate(relative.theme.dist = within/between)

ms = all.dists.item.ms.gp %>%
  left_join(select(dict, -type), by=c("item1" = "item")) %>%
  rename(theme1 = theme) %>%
  group_by(theme1, group) %>%
  multi_boot_standard(column = "relative.theme.dist") %>%
  mutate(group = fct_relevel(group, "young", "middle", "old", "adult")) 

ggplot(ms, aes(x = group, y = mean)) +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  facet_wrap(~theme1) +
  theme_bw()


### TYPE
all.dists.item.ms = all.dists %>%
    group_by(item1, type2, group) %>%
    summarize(mean = mean(dist)) 
    
all.dists.item.ms.gp = all.dists.item.ms %>%
  left_join(dict, by=c("item1" = "item")) %>%
  rename(type1 = type,
         theme1 = theme) %>%
  select(group, item1, type1, type2, mean) %>%
  mutate(category = ifelse(type1 == type2, "within", "between")) %>%
  ungroup() %>%
  select(-type1, -type2) %>%
  group_by(group, item1) %>%
  spread(category, mean) %>%
  mutate(relative.type.dist = within/between)

ms = all.dists.item.ms.gp %>%
  left_join(select(dict, -theme), by=c("item1" = "item")) %>%
  rename(type1 = type) %>%
  group_by(type1, group) %>%
  multi_boot_standard(column = "relative.type.dist") %>%
  mutate(group = fct_relevel(group, "young", "middle", "old", "adult")) 

ggplot(ms, aes(x = group, y = mean)) +
  geom_bar(stat ="identity") +
  geom_linerange(aes(ymax = ci_upper, ymin = ci_lower)) +
  facet_wrap(~type1) +
  theme_bw()
```



