---
title: Plot embeddings from Next Pilot
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: true
    code_folding: hide 
---

******
******


```{r setup, include = F}
# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(ggplot2)
library(stringr)
library(forcats)
library(jsonlite)


opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = F, tidy = F, fig.height = 4)
```  

## Read in raw trial data 
```{r}
p1_young= read.csv("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot1/data/next/3-4yo/participant_data_34.csv") %>%
  mutate(exp = 1, 
         age_group = "young")
p1_mid= read.csv("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot1/data/next/5-6yo/participant_data_56.csv") %>%
  mutate(exp = 1,
         age_group = "mid")
p2_young= read.csv("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot2/data/3-4yo/participant_data_34.csv") %>%
  mutate(exp = 2,
         age_group = "young")
p2_mid= read.csv("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot2/data/5-6yo/participant_data_56.csv") %>%
  mutate(exp = 2,
         age_group = "mid")

p2_old= read.csv("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot2/data/7-8yo/participant_data_78.csv") %>%
  mutate(exp = 2,
         age_group = "old")
```

Merge and munge
```{r}
d = rbind(p1_young, p1_mid, p2_young, p2_mid, p2_old) %>%
    filter(alg_id == "UncertaintySampling") %>%
    mutate(participant_uid, subid = lapply(str_split(participant_uid, "_"), 
                                   function(x) {x[2]})) %>%
    select(exp, subid, age_group, target_center, target_left, target_right, target_winner) %>%
    mutate_each(funs(lapply(str_split(., ".com/|.jpg"), 
                                   function(x) {x[2]})), -exp, -age_group, -subid)  %>%
    mutate_each(funs(as.factor(unlist(.))),-exp, -age_group)  %>%
    mutate(age_group = fct_relevel(age_group, "young", "mid")) 


d = filter(d, subid != "7smVlvhKMXzrayO8MtwFKuo23EWP9N")
```

## Demographics
### Number of participants
```{r}
d %>%
  group_by(subid, age_group,exp) %>%
  slice(1) %>%
  group_by(exp, age_group) %>%
  summarize(n = n())  %>%
  kable()
```

### Number of trials
```{r}
d %>%
  group_by(exp, age_group) %>%
  summarize(n = n())  %>%
  kable()
```


## Munge data for python
Convert names to numeric (for python)
```{r}
#images = unique(d$i)
#image_dict = data.frame(images = images, image_num = 0:(length(images)-1))
#write.csv(image_dict, "image_dict.csv", row.names = F)
image_dict = read.csv("image_dict.csv")
```

```{r}
d = d %>%
    mutate(i = target_center,
           j = ifelse(target_left == target_winner, as.character(target_right), as.character(target_left)),
           k = target_winner)

d_numeric = d %>%
  select(exp, age_group, i, j, k) %>%
  left_join(select(image_dict, images, image_num), by=c("i"="images")) %>%
  select(-i) %>%
  rename(i = image_num) %>%
  left_join(select(image_dict, images, image_num), by=c("j"="images")) %>%
  select(-j) %>%
  rename(j = image_num) %>%
  left_join(select(image_dict, images, image_num), by=c("k"="images")) %>%
  select(-k) %>%
  rename(k = image_num)
```

Save for python
```{r, eval = F}
write.csv(d_numeric, "triplet_data.csv", row.names = F)
```

Run get_embeddings.ipynb to get embeddings (computeEmbeddings python)
`jupyter notebook get_embeddings.ipynb`.

## Embeddings
###  Uncertainty E1 and E2  {.tabset}
```{r}
es = read.csv("all_embeddings_uncertainty.csv") %>%
  rename(image_num = X.1) %>%
  mutate(age_group = fct_relevel(age_group, "young", "mid")) %>%
  left_join(image_dict)
```

#### Points
```{r}
ggplot(es, aes(x = X, y = Y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        legend.position = "bottom")

```

#### Labels
```{r}
ggplot(es, aes(x = X, y = Y)) +
   geom_text(aes(label=images), size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```

### All E1 and E2 {.tabset}
```{r}
es = read.csv("all_embeddings_all.csv") %>%
  rename(image_num = X.1) %>%
  mutate(age_group = fct_relevel(age_group, "young", "mid")) %>%
  left_join(image_dict)
```

#### Points
```{r}
ggplot(es, aes(x = X, y = Y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        legend.position = "bottom")

```

#### Labels
```{r}
ggplot(es, aes(x = X, y = Y)) +
   geom_text(aes(label=images), size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```


### Uncertainty E2 {.tabset}
```{r}
es = read.csv("all_embeddings_2_uncertainty.csv") %>%
  rename(image_num = X.1) %>%
  mutate(age_group = fct_relevel(age_group, "young", "mid")) %>%
  left_join(image_dict)
```

#### Points
```{r}
ggplot(es, aes(x = X, y = Y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        legend.position = "bottom")

```

#### Labels
```{r}
ggplot(es, aes(x = X, y = Y)) +
   geom_text(aes(label=images), size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```

### Uncertainty E2 {.tabset}
```{r}
es = read.csv("all_embeddings_uncertainty_withall.csv") %>%
  rename(image_num = X.1) %>%
  filter(age_group == "all_groups") %>% 
  left_join(image_dict)
```

#### Points
```{r}
ggplot(es, aes(x = X, y = Y, color = type, shape = theme)) +
   geom_point(size = 3) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        legend.position = "bottom")

```

#### Labels
```{r}
ggplot(es, aes(x = X, y = Y)) +
   geom_text(aes(label=images), size = 3) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```


### Next Uncertainty E2 {.tabset}
```{r}
p2e_young= flatten(fromJSON("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot2/data/3-4yo/embedding_34_uncertainty.txt")) %>%
  select(darray, target.alt_description) %>%
  mutate(exp = 2,
         age_group = "young")

p2e_mid= flatten(fromJSON("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot2/data/5-6yo/embedding_56_uncertainty.txt"))%>%
    select(darray, target.alt_description) %>%
    mutate(exp = 2,
         age_group = "mid")

p2e_old= flatten(fromJSON("/Documents/GRADUATE_SCHOOL/Projects/next_kids/experiments/nextKids_pilot2/data/7-8yo/embedding_78_uncertainty.txt"))%>%
    select(darray, target.alt_description) %>%
    mutate(exp = 2,
         age_group = "old")

next_embed = rbind(p2e_young, p2e_mid, p2e_old) %>%
    mutate(images = unlist(lapply(str_split(target.alt_description, ".jpg"), 
                                   function(x) {x[1]}))) %>%
   select(-target.alt_description) %>%
   separate(darray, c("X", "Y"), ",") %>%
   mutate(X = as.numeric(gsub( "c\\(", "", X)),
          Y = as.numeric(gsub("\\)", "", Y)),
          age_group = as.factor(age_group),
          images = as.factor(images)) %>%
    mutate(age_group = fct_relevel(age_group, "young", "mid")) %>%
    left_join(image_dict) %>%
    select(-image_num)
```

#### Points
```{r}
ggplot(next_embed, aes(x = X, y = Y, color = type, shape = theme)) +
   geom_point(size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank(),
        legend.position = "bottom")
```

#### Labels
```{r}
ggplot(next_embed, aes(x = X, y = Y)) +
   geom_text(aes(label=images), size = 3) +
   facet_wrap(~age_group) +
   theme_bw() +
   theme(panel.grid.major = element_blank(),
        panel.grid.minor = element_blank(),
        strip.text.x = element_text(size = 14),
        strip.background = element_rect(colour="grey", fill="grey"),
        axis.title=element_blank(),
        axis.text=element_blank(),
        axis.ticks=element_blank())
```
