---
title: NextKids pilot - prep raw responses for embeddings
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: true
    code_folding: hide 
---

******
******

```{r setup, include = F}
# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(ggplot2)
library(stringr)
library(forcats)
library(jsonlite)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = T, tidy = F, fig.height = 4)
```  

## read in embeddings
```{r}
young = read.csv("../../data/pilot1_and_2/participant_data_pilot_1_2_34.csv") %>%
  mutate(exp = "young")
middle = read.csv("../../data/pilot1_and_2/participant_data_pilot_1_2_56.csv")  %>%
  mutate(exp = "middle")
old = read.csv("../../data/pilot1_and_2/participant_data_pilot_1_2_78.csv")  %>%
  mutate(exp = "old")
adult = read.csv("../../data/adult/participant_data_adult.csv")  %>%
  mutate(exp = "adult")
```

Put in format of "example-responses.csv"
```{r}
d = rbind(young, middle) %>%
   rbind(old) %>%
  rbind(adult) %>%
  select(X, timestamp_query_generated, participant_uid, target_center, target_left, target_right, target_winner, alg_label,response_time, exp)

d = d %>%
     mutate(Participant.ID.sub = lapply(str_split(participant_uid, "_"), 
                                   function(x) {x[2]}),
            participant_uid = tolower(participant_uid)) %>%
      mutate_each(funs(lapply(str_split(., ".com/"), 
                                   function(x) {x[2]})), target_center, target_left, target_right, target_winner) 

d.munged = d %>%
  rename(Timestamp = timestamp_query_generated,
         Participant.ID = participant_uid,
         Center = target_center,
         Left = target_left,
         Right = target_right,
         Answer = target_winner,
         Alg.Label = alg_label,
         Response.Time..s. = response_time,
         Condition = exp) %>%
  mutate(Session = Condition) %>%
  select(Participant.ID,	Timestamp,	Center,	Left,	Right,	Answer,	Alg.Label,	Response.Time..s.,	Participant.ID.sub,	Condition,	Session) %>%
  mutate_each(funs(as.factor(unlist(.))))  %>%
  mutate(Timestamp = "2017-01-01 07:35:01.01") #this is just a random time so the date is in the right format for the python script

## remove other tral types from pilot1
d.munged = d.munged %>%
  filter(Alg.Label == "RandomSampling" | Alg.Label =="UncertaintySampling") 

```

## young-middle-old age groups
```{r}
write.csv(filter(d.munged, Condition == "young"), "participant_data_pilot_1_2_34M.csv")
write.csv(filter(d.munged, Condition == "middle"), "participant_data_pilot_1_2_56M.csv")
write.csv(filter(d.munged, Condition == "old"), "participant_data_pilot_1_2_78M.csv")
write.csv(filter(d.munged, Condition == "adult"), "participant_data_pilot_adultM.csv")

```

## Median split on age
```{r}
demo = read.csv("../../data/pilot1_and_2/nextKids_1_2_combined_other_data.csv")

demo = demo %>%
  mutate(total_words= ifelse(total_words == 0 | age_group == "old", NA, total_words))
```

```{r}
MEDIAN.AGE = median(demo$age, na.rm = T)
MEDIAN.VOCAB = median(demo$total_words, na.rm = T)
      
demo = demo %>%
        mutate(age.median = ifelse(age > MEDIAN.AGE, "high", "low"),
              age.median = as.factor(age.median),
              vocab.median = ifelse(total_words > MEDIAN.VOCAB , "high", "low"),
              vocab.median= as.factor(vocab.median))
```

```{r}
d.age = d.munged %>%
  left_join(select(demo, subid, age.median), by = c("Participant.ID.sub" = "subid"))

write.csv(filter(d.age, age.median == "low") %>% select(-age.median), "participant_data_pilot_1_2_lowageM.csv")
write.csv(filter(d.age, age.median == "high") %>% select(-age.median), "participant_data_pilot_1_2_highageM.csv")
```

## Median split on vocab
```{r}
d.vocab = d.munged %>%
  left_join(select(demo, subid, vocab.median), by = c("Participant.ID.sub" = "subid"))

write.csv(filter(d.vocab, vocab.median == "low") %>% select(-vocab.median), "participant_data_pilot_1_2_lowvocabM.csv")
write.csv(filter(d.vocab, vocab.median == "high") %>% select(-vocab.median), "participant_data_pilot_1_2_highvocabM.csv")
```



To get embeddings:
(1) cd /Documents/GRADUATE_SCHOOL/Projects/next_kids/embedding_code/condortools
(2) update stub.yaml
(3) python expandStub_yaml.py stub.yaml
(4) python setupJobs_yaml.py master.yaml
(5) python ../nextmds/generateEmbedding.py 0
(6) Move 0/ folder to analysis folder with stub.yaml

