---
title: NextKids pilot - prep raw responses for embeddings
author: Molly Lewis 
date: "`r Sys.Date()`"
output: 
  html_document:
    toc: true
    number_sections: false
    theme: cerulean
    toc_float: true
    code_folding: hide 
---

******
******

```{r setup, include = F}
# load packages
library(knitr)
library(rmarkdown)
library(broom)
library(tidyverse) 
library(ggplot2)
library(stringr)
library(forcats)
library(jsonlite)
library(magrittr)

opts_chunk$set(echo = T, message = F, warning = F, 
               error = F, cache = T, tidy = F, fig.height = 4)
```  

## read in raw responses
```{r}
young = read.csv("../../../data/pilot1_and_2/participant_data_pilot_1_2_34.csv") %>%
  mutate(exp = "young")
middle = read.csv("../../../data/pilot1_and_2/participant_data_pilot_1_2_56.csv")  %>%
  mutate(exp = "middle")
old = read.csv("../../../data/pilot1_and_2/participant_data_pilot_1_2_78.csv")  %>%
  mutate(exp = "old")
adult = read.csv("../../../data/adult/participant_data_adult.csv")  %>%
  mutate(exp = "adult")
```

Put in format of "example-responses.csv"
```{r}
d = rbind(young, middle) %>%
    rbind(old) %>%
    rbind(adult) %>%
    select(X, timestamp_query_generated, participant_uid, target_center, target_left, target_right, target_winner, alg_label,response_time, exp)

d %<>%
     mutate(Participant.ID.sub = lapply(str_split(participant_uid, "_"), 
                                   function(x) {x[2]}),
            participant_uid = tolower(participant_uid)) %>%
      mutate_each(funs(lapply(str_split(., ".com/"), 
                                   function(x) {x[2]})), target_center, target_left, target_right, target_winner) 

d.munged = d %>%
  rename(Timestamp = timestamp_query_generated,
         Participant.ID = participant_uid,
         Center = target_center,
         Left = target_left,
         Right = target_right,
         Answer = target_winner,
         Alg.Label = alg_label,
         Response.Time..s. = response_time,
         Condition = exp) %>%
  mutate(Session = Condition) %>%
  select(Participant.ID,	Timestamp,	Center,	Left,	Right,	Answer,	Alg.Label,	Response.Time..s.,	Participant.ID.sub,	Condition,	Session) %>%
  mutate_each(funs(as.factor(unlist(.))))  %>%
  mutate(Timestamp = "2017-01-01 07:35:01.01") #this is just a random time so the date is in the right format for the python script

## remove other tral types from pilot1
d.munged = d.munged %>%
  filter(Alg.Label == "RandomSampling" | Alg.Label =="UncertaintySampling") 

```

## Median split on naming
```{r}
demo = read.csv("../../../data/pilot1_and_2/nextKids_1_2_combined_other_data.csv") %>%
  mutate(total_words = ifelse(total_words == 0 | age_group == "old", NA, total_words)) %>%
  select(-X)
```

Medin split based on exact match of intended label (naming1)
```{r}
name = read.csv("../../../data/other/AnimalNaming_04032017.csv")
name1  = name %>%  
         mutate(isCorrect = ifelse(response == as.character(animals),1,0))

name.summary = name1 %>%
  group_by(subjCode) %>%
  summarize(prop.naming.correct = sum(isCorrect)/n()) %>%
  mutate(subid = tolower(subjCode)) %>%
  select(-subjCode)

MEDIAN.NAMING = median(name.summary$prop.naming.correct, na.rm = T)

name.summary %<>% mutate(name.median.1 = ifelse(prop.naming.correct > MEDIAN.NAMING,
                                              "high", "low"),
                         name.median.1 = as.factor(name.median.1))

demo %<>%
  left_join(name.summary %>% select(subid, name.median.1))
```

Median split counting -ie as correct (pig == piggie) (naming2)
```{r}
name2 = name %>% 
        mutate(ie_word = ifelse(str_sub(response, start= -2) == "ie", 1, 0),
              isCorrect = ifelse(response == as.character(animals) | ie_word == 1, 1, 0))


name.summary2 = name2 %>%
  group_by(subjCode) %>%
  summarize(prop.naming.correct = sum(isCorrect)/n()) %>%
  mutate(subid = tolower(subjCode)) %>%
  select(-subjCode)

MEDIAN.NAMING = median(name.summary$prop.naming.correct, na.rm = T)

name.summary2 %<>% mutate(name.median.2 = ifelse(prop.naming.correct > MEDIAN.NAMING,
                                              "high", "low"),
                         name.median.2 = as.factor(name.median.2))

demo %<>%
  left_join(name.summary2 %>% select(subid, name.median.2))
```

```{r}
d.naming = d.munged %>%
  left_join(select(demo, subid, name.median.2, name.median.1), by = c("Participant.ID.sub" = "subid")) %>%
  filter(!is.na(name.median.2) & !is.na(name.median.1))

write.csv(filter(d.naming, name.median.1 == "low") %>% select(-name.median.1, -name.median.2), "participant_data_pilot_1_2_low_naming1M.csv")

write.csv(filter(d.naming, name.median.1 == "high") %>% select(-name.median.1, -name.median.2), "participant_data_pilot_1_2_high_naming1M.csv")

write.csv(filter(d.naming, name.median.2 == "low") %>% select(-name.median.1, -name.median.2), "participant_data_pilot_1_2_low_naming2M.csv")

write.csv(filter(d.naming, name.median.2 == "high") %>% select(-name.median.1, -name.median.2), "participant_data_pilot_1_2_high_naming2M.csv")
```


To get embeddings:
(1) cd /Documents/GRADUATE_SCHOOL/Projects/next_kids/embedding_code/condortools
(2) update stub.yaml manually with correct path
(3) python expandStub_yaml.py stub.yaml
(4) python setupJobs_yaml.py master.yaml
(5) python ../nextmds/generateEmbedding.py 0
(6) Move 0/ folder to analysis folder with stub.yaml

